Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-03 article.tex
MINOR: added the word "windowing" before "semantics" in start of WC-Datalog

\begin{nestedsection}{Windowed Continuous Datalog}{semantics}
The first requirement of stream reasoning is a well-defined semantics
that takes into account both the continuous nature of a subset of the
base axioms of a stream reasoning problem, as well as its
instantaneous truth and entailments, in line with the work of the
reasoning community.  However, it must also provide a continuous
interpretation of those instantaneous entailments in order to
integrate with other stream-processing technologies.  More
specifically, an appropriate semantics for stream reasoning on the
Semantic Web must: allow the expression of OWL 2 ontologies to some
degree of expressivity; not sacrifice the precise semantics thereof
whilst incorporating the semantics of stream processing; and allow for
the continuous derivation of entailments in a concise manner.

>>>>

\begin{nestedsection}{Windowed Continuous Datalog}{semantics}
The first requirement of stream reasoning is a well-defined semantics
that takes into account both the continuous nature of a subset of the
base axioms of a stream reasoning problem, as well as its
instantaneous truth and entailments, in line with the work of the
reasoning community.  However, it must also provide a continuous
interpretation of those instantaneous entailments in order to
integrate with other stream-processing technologies.  More
specifically, an appropriate semantics for stream reasoning on the
Semantic Web must: allow the expression of OWL 2 ontologies to some
degree of expressivity; not sacrifice the precise semantics thereof
whilst incorporating the windowing semantics of stream processing; and allow for
the continuous derivation of entailments in a concise manner.
